Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-11 Manuscript.Rmd
Updated meta-analysis and roi plots, now onto correlation vs FV, which shows negative corrs for some reason

```{r Template partition (Fig. 2), out.width="50%", fig.align = "center", fig.cap = "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
include_graphics("./Images/newPattern_both.png")
```

``` {r Partition comparison: all cross-method agreement (Fig. 3), fig.align="center", fig.width=3.5, fig.height=3.5, echo=FALSE, message = FALSE, fig.cap = "Figure 3. Distribution of ARI indices when comparing modularity and spectral partitioning. The distribution shows overall high agreement. (Will probably remove this figure)"}
RI_within_plot <- ggplot(data = RI_all_within, aes(Index)) + 
        geom_density(fill = Cols[3]) + 
        xlim(0,1) + 
        labs(x = "Adj. Rand Index") +
        theme_classic()
RI_within_plot
```

@@

``` {r Stability per subject: Overall (Fig. 9), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 9. ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE}
# TAKE THE TIME TO BRING THE GGPLOT DEFINITION DOWN HERE EVENTUALLY
grid.arrange(SC_plot, SC_sd_plot, ncol = 2)
```

>>>>

```{r Template partition (Fig. 2), out.width="50%", fig.align = "center", fig.cap = "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
include_graphics("./Images/FB_FV_example.png")
```

@@
